Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-05-11 WSSSPE4_report/WSSSPE4_paper.tex
small tweaks

After most of the lightning talks and other presentations, WSSSPE used three areas of a large room to let
attendees use sticky flip charts and sticky notes on the walls to suggest
\begin{enumerate}
\item A vision on any aspect of the work
\item A gap or challenge
\item A project idea
\end{enumerate}
(with one area of the room for each topic.)
%
Next, attendees organically formed groups around the flip charts on the wall\footnote{Photos of the flipcharts: \url{https://github.com/WSSSPE/media/tree/master/WSSSPE4-photos}}.  This led to the 12 groups that are discussed in the rest of this section.
The groups then worked in Google docs, and eventually created Google slides to show their work back to the larger groups. The docs and slides were stored in a common Google Drive folder\footnote{\url{https://drive.google.com/drive/u/0/folders/0BzIpChHwv-q5X3lRaWhYMXJZaUE}}.

%\todo{need to confirm who will write Access subsection (\S\ref{sec:access})}

@@

\begin{itemize}
\item Join our Google Group/mailing list
  \cite{WSSSPEUndergradGoogleGroup}.
\item Join the WSSSPE Slack (\S\ref{sec:slack}) and the
  \texttt{\#wg-undergraduatecourse} channel.
\item Ask to join the WSSSPE4-undergraduate-course organization
  \cite{WSSSPEUndergradGithub}.
\end{itemize}

@@

Each developer of software with uncommon needs (hardware, software, libraries, data sets), non-public code, or tests that exceed time limits for free plans must acquire, setup, and maintain their own continuous integration systems because their needs make them ineligible for popular free services such as Travis CI.  For example, software groups that develop BIOUNO, CI4SI, or GROMACS have done this.
(Note that Debian provides a testing infrastructure (\url{https://ci.debian.net/doc/}) that is mature and supports hardware and other requirement specifications.)

>>>>

After most of the lightning talks and other presentations, WSSSPE used three areas of a large room to let
attendees use sticky flip charts and sticky notes on the walls to suggest: (1) a vision on any aspect of the work, (2) a gap or challenge, or (3) a project idea.
Next, attendees organically formed groups around the flip charts on the walls.  This led to the 12 groups that are discussed in the rest of this section.
Summaries of each group's activities follow; for more details
about the group discussions see \cite{WSSSPE4-report}.

@@

\begin{itemize}
\item Join the Google Group/mailing list
  \cite{WSSSPEUndergradGoogleGroup}.
\item Join the WSSSPE Slack (\S\ref{sec:slack}) and the
  \texttt{\#wg-undergraduatecourse} channel.
\item Ask to join the WSSSPE4-undergraduate-course organization
  \cite{WSSSPEUndergradGithub}.
\end{itemize}

@@

Each developer of software with uncommon needs (hardware, software, libraries, data sets), non-public code, or tests that exceed time limits for free plans must acquire, setup, and maintain their own continuous integration systems because their needs make them ineligible for popular free services such as Travis CI.  For example, software groups that develop BIOUNO, CI4SI, or GROMACS have done this.
(Note that Debian provides a testing infrastructure\footnote{\url{https://ci.debian.net/doc/}} that is mature and supports hardware and other requirement specifications.)
